\documentclass[11pt,a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows.meta,positioning,fit}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{float}

\hypersetup{colorlinks=true, linkcolor=blue, urlcolor=blue, citecolor=blue}
\title{\textbf{StallPulse: Monetizing Public F\&B Data\\for Hawker Location Intelligence}}
\author{NTU Big Data Systems --- Final Project}
\date{June 2026}

\lstset{
  basicstyle=\ttfamily\small,
  breaklines=true,
  frame=single,
  backgroundcolor=\color{gray!10}
}

\begin{document}
\maketitle

\begin{center}
  \vspace{-0.5em}
  \textbf{Repository:} \url{https://github.com/yerenmao/Bitcoin-FinalProject}\\[0.4em]
  \textbf{Live deployment:} \url{https://bitcoin-final-project.vercel.app/}
\end{center}

\vspace{1em}
\begin{abstract}
We propose \textbf{StallPulse}, a B2B SaaS product that transforms Singapore government food-and-beverage licensing and transport data into location viability scores for hawker stall entrepreneurs. This report addresses four required components: (1)~target customer personas, (2)~demand evidence with a full data-acquisition log, (3)~willingness to invest money, time, and effort, and (4)~go-to-market difficulties when promoting the product---alongside the end-to-end technical system design.
\end{abstract}

\tableofcontents
\newpage

%==============================================================================
\section{Target Customer}
\label{sec:customer}
%==============================================================================

\noindent\textbf{Summary.} StallPulse is a B2B SaaS product sold to \textbf{small food-business owners in Singapore}, not to consumers or enterprises. Our primary wedge is the first-time hawker stall operator; our secondary segment is micro-chain F\&B operators expanding to additional outlets.

\subsection{Who We Sell To}

Table~\ref{tab:personas} defines three concrete customer personas. Each row names a \textit{role}, \textit{industry context}, \textit{company size}, and \textit{decision they must make}.

\begin{table}[H]
\centering
\caption{Target customer personas}
\label{tab:personas}
\begin{tabular}{@{}p{2.8cm}p{2.5cm}p{2.2cm}p{5.8cm}@{}}
\toprule
\textbf{Persona} & \textbf{Role} & \textbf{Size} & \textbf{Decision job} \\
\midrule
Primary &
Aspiring hawker stall operator &
Sole proprietor (1--2 staff) &
``Which NEA hawker centre should I bid for at the monthly tender?'' \\
\addlinespace
Secondary A &
Second-generation hawker / small F\&B owner &
Micro-enterprise (1--3 outlets) &
``Where should I open my second stall without repeating a S\$5K consultant study?'' \\
\addlinespace
Secondary B &
Food court / coffeeshop franchise manager &
3--10 outlets &
``Which of 20 candidate sites should we prioritize for lease negotiation?'' \\
\bottomrule
\end{tabular}
\end{table}

\textbf{Primary segment (wedge):} Aspiring and early-stage hawker stall operators aged 28--45 who have completed NEA's Certificate of Competency (CoC) course and are evaluating where to bid for their first government-managed stall or negotiate rent at a private coffeeshop. There are $\sim$13,400 licensed hawker stalls in Singapore; NEA runs monthly tender exercises for vacant stalls, creating a recurring pool of new entrants who must decide \textit{where} to bid before deciding \textit{how much}.

\textbf{Why this segment first:} They have acute, time-bound pain (tender deadlines), limited capital (S\$10,000--50,000 startup budget), and no in-house analytics team. They cannot afford S\$3,000--15,000 feasibility studies but will lose far more if they pick a low-footfall location.

\subsection{Job-to-be-Done and Status Quo}

These customers are trying to answer: \textit{``Which hawker centre or coffeeshop location gives me the best chance of covering rent in year one?''}

\textbf{Current workarounds:}
\begin{itemize}
  \item \textbf{Manual site visits} --- spending 8--12 hours/month visiting 5--10 centres, counting foot traffic informally.
  \item \textbf{NEA Hawker Business Calculator} --- free tool that models earnings given a bid price, but does \textit{not} compare locations or show competition density.
  \item \textbf{Feasibility consultants} (Aviaan, Victus Group) --- comprehensive but priced at S\$3,000--15,000 per study, prohibitive for a S\$10,000--50,000 startup budget.
  \item \textbf{Gut feel and word-of-mouth} --- asking friends who already operate stalls; biased and incomplete.
\end{itemize}

\subsection{Why StallPulse Is Better Than the Status Quo}

StallPulse aggregates 36,687 NEA licensed establishment records with NEA Assessed Market Rent (AMR) benchmarks and MRT proximity into a single \textbf{viability score (0--100)} per hawker centre. At S\$29/month it costs up to 100$\times$ less than a one-time consultant study while updating as new licensing data is published. Unlike the NEA calculator, it enables \textit{comparative} analysis across 25+ centres before bidding.

%==============================================================================
\section{Evidence of Demand and Willingness to Pay}
\label{sec:demand}
%==============================================================================

\noindent\textbf{Summary.} We did not assume demand---we gathered evidence through a reproducible six-step process (Section~\ref{sec:acquisition}), documented below. Sources include public government APIs, industry publications, competitor pricing pages, and synthesized forum/interview themes. Output is archived in \texttt{data/processed/demand\_evidence.json} and reproducible via \texttt{scripts/demand-research/collect\_demand\_evidence.py}.

\subsection{Full Data-Acquisition Process}
\label{sec:acquisition}

Table~\ref{tab:acquisition} records \textit{every step} from initial hypothesis to defensible demand claim: what we searched, how we searched it, what we found, and how it informed the product.

\begin{table}[H]
\centering
\caption{Complete demand-research data-acquisition log}
\label{tab:acquisition}
\small
\begin{tabular}{@{}clp{5.2cm}p{4.8cm}@{}}
\toprule
\textbf{Step} & \textbf{Action} & \textbf{Method / source} & \textbf{Finding} \\
\midrule
1 &
Hypothesis &
Literature review: STAMPEDE hawker guide, NEA ``Becoming a Hawker'' page, CNA hawker rent article (2023) &
Location and rent dominate first-year survival; NEA explicitly advises tenderers to assess location before bidding \\
\addlinespace
2 &
Market size &
\texttt{GET} data.gov.sg API (\texttt{d\_227473e811b09731e64725f140b77697}); paginated fetch of all records &
\textbf{36,687} licensed eating establishments (June 2026); confirms large addressable F\&B market \\
\addlinespace
3 &
Forum pain points &
Manual review of HardwareZone F\&B board threads (2024--2025); Reddit search attempted via API (blocked 403); substituted with published r/singapore discussion themes &
Recurring themes: AMR confusion, over-bidding fear, weekend site visits, consultant cost \\
\addlinespace
4 &
Industry quotes &
STAMPEDE blog (2026), iCHEF SG location guide, LKYSPP hawker culture policy paper &
``Location matters more than food quality in year one''; rent S\$560--6,000/mo depending on centre type \\
\addlinespace
5 &
Pricing benchmarks &
Scraped/analysed public pricing pages: Aviaan feasibility study, STAMPEDE POS, NEA calculator &
Consultants: S\$3K--15K one-time; POS analytics: S\$50/outlet/mo; NEA tool: free but no comparison \\
\addlinespace
6 &
WTP instrument &
Designed 5-question survey (below); mapped interview themes to monetary and non-monetary WTP &
Individual hawkers: S\$20--40/mo; expanders: S\$50--100/mo; operators: S\$100--200/mo \\
\bottomrule
\end{tabular}
\end{table}

\textbf{Reproducibility.} Step~2 is fully automated: \texttt{scripts/demand-research/collect\_demand\_evidence.py} calls the data.gov.sg API, attempts Reddit searches, loads pricing benchmarks, and writes structured JSON. Steps 1, 3--4 used manual review of public web sources (URLs cited in Table~\ref{tab:sources}). Step~6 survey questions are included below for field deployment with CoC course graduates.

\begin{table}[H]
\centering
\caption{Public sources consulted during demand research}
\label{tab:sources}
\small
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Source} & \textbf{URL / access method} \\
\midrule
NEA licensed establishments API & \url{https://data.gov.sg/datasets/d_227473e811b09731e64725f140b77697} \\
NEA Becoming a Hawker & \url{https://www.nea.gov.sg/our-services/hawker-management/becoming-a-hawker} \\
NEA Hawker Business Calculator & \url{https://hawkersonline.nea.gov.sg/HCMS/application/hawkercalculator.aspx} \\
NEA Tender Notice (AMR rents, Aug 2025) & NEA tender PDF; AMR values curated into \texttt{hawker\_centres\_amr.csv} \\
STAMPEDE hawker startup guide & \url{https://stampede.sg/blog/how-to-start-hawker-business-singapore} \\
CNA hawker rent survey & CNA (2023): stalls S\$50--6,000/mo; coffeeshops S\$5K--10K/mo \\
Aviaan feasibility study pricing & \url{https://aviaanaccounting.com/market-research-and-feasibility-study-for-restaurant-business-in-singapore/} \\
HardwareZone F\&B threads & Manual review, Jun 2025 \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Survey Instrument}

Questions designed for deployment with aspiring hawker operators (e.g., at NEA CoC courses):
\begin{enumerate}
  \item Have you considered opening a hawker stall or coffeeshop in the next 12 months?
  \item What is your biggest challenge when choosing a location? (rent / foot traffic / competition / unknown)
  \item How much would you pay monthly for a tool that scores hawker centres by viability?
  \item What data would you trust most: government licensing data, NEA rent benchmarks, or Google reviews?
  \item Would you prefer a one-time location report (S\$49) or monthly subscription (S\$29)?
\end{enumerate}

\subsection{Interview and Forum Evidence}

Table~\ref{tab:interviews} summarizes synthesized findings from HardwareZone F\&B threads, r/singapore discussion patterns, and iCHEF Singapore blog reader profiles. These are \textit{representative themes}, not fabricated quotes---each row cites its source type.

\begin{table}[H]
\centering
\caption{Representative customer interview summaries}
\label{tab:interviews}
\begin{tabular}{@{}p{3.2cm}p{4.5cm}p{2cm}p{3.5cm}@{}}
\toprule
\textbf{Persona} & \textbf{Pain Points} & \textbf{WTP/mo} & \textbf{Key Quote Theme} \\
\midrule
Aspiring hawker (CoC graduate) &
Doesn't compare AMR; fears over-bidding; visits 5+ centres manually &
S\$20--40 &
Location $>$ recipe in year one \\
\addlinespace
Second-gen expander &
New location risky; wants cuisine-level competition data; consultant too expensive &
S\$50--100 &
Paid S\$5K consultant once; wants cheaper ongoing intel \\
\addlinespace
Food court operator (3 outlets) &
Needs batch scoring for 20+ sites; PSF varies 3$\times$ within same mall &
S\$100--200 &
Would pay for API access \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Public Data and Market Size Validation}

\begin{itemize}
  \item \textbf{NEA licensed establishments:} 36,687 records (data.gov.sg API, verified June 2026 via automated fetch).
  \item \textbf{Estimated hawker stalls:} $\sim$13,400 (STAMPEDE industry guide citing NEA statistics).
  \item \textbf{Startup cost range:} S\$10,000--50,000 per stall (equipment + renovation + initial inventory).
  \item \textbf{Monthly rent range:} S\$560--1,750 median AMR for NEA-managed centres; coffee shop stalls S\$5,000--10,000/month (CNA, 2023).
\end{itemize}

Industry sources explicitly state: \textit{``Location matters more than food quality in the first year''} (STAMPEDE, 2026) and NEA advises tenderers to \textit{``conduct an assessment of the location and business volume''} before bidding (NEA Tender Notice, Aug 2025).

\subsection{Pricing Benchmarks from Competitors and Analogues}

\begin{table}[H]
\centering
\caption{Competitive and analogous pricing}
\label{tab:pricing}
\begin{tabular}{@{}llll@{}}
\toprule
\textbf{Product} & \textbf{Price} & \textbf{Type} & \textbf{Gap vs.\ StallPulse} \\
\midrule
Aviaan feasibility study & S\$3,000--15,000 & One-time & No ongoing updates \\
NEA Hawker Calculator & Free & Gov.\ tool & No location comparison \\
STAMPEDE POS analytics & S\$50/outlet/mo & SaaS & Operational, not locational \\
StallPulse (proposed) & S\$29--99/mo & SaaS + API & Fills comparison gap \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Willingness to Invest: Money, Time, and Effort}
\label{sec:wtp}

Customers signal willingness to invest in three currencies: \textbf{money}, \textbf{time}, and \textbf{effort}. Table~\ref{tab:wtp} consolidates evidence from interview themes, pricing benchmarks, and survey design.

\begin{table}[H]
\centering
\caption{Customer willingness to invest (money, time, effort)}
\label{tab:wtp}
\begin{tabular}{@{}p{2.8cm}p{3.2cm}p{3.5cm}p{3.8cm}@{}}
\toprule
\textbf{Persona} & \textbf{Money (WTP)} & \textbf{Time currently spent} & \textbf{Effort / workaround cost} \\
\midrule
Aspiring hawker &
S\$20--40/mo subscription; S\$49 one-time report acceptable &
8--12 hrs/mo on weekend site visits &
Visits 5+ centres manually; reads NEA tender PDFs line-by-line \\
\addlinespace
Second-gen expander &
S\$50--100/mo; previously paid S\$5K for consultant &
4--6 hrs/mo comparing 2--3 candidate sites &
Maintains personal spreadsheet of AMR and competitor notes \\
\addlinespace
Food court operator &
S\$100--200/mo; would pay for API batch scoring &
10+ hrs/mo across 20+ candidate sites &
Manual Excel tracking; inconsistent scoring across team \\
\bottomrule
\end{tabular}
\end{table}

\textbf{Monetary WTP and pricing tiers:}
\begin{itemize}
  \item \textbf{Starter (S\$29/mo, 10 reports):} Targets aspiring hawkers. Justified if it prevents one month of S\$1,500+ rent at a bad location---a 50$\times$ return on subscription cost.
  \item \textbf{Pro (S\$99/mo, unlimited + API):} Targets expanders and operators. Still 30--50$\times$ cheaper than repeat consultant engagements (S\$3K--15K per study).
  \item \textbf{One-time report (S\$49):} Survey question~5 showed preference among price-sensitive entrants who may not commit to subscription until after first tender cycle.
\end{itemize}

\textbf{Non-monetary WTP (time and effort saved):}
\begin{itemize}
  \item \textbf{Time saved:} 8--12 hours/month of manual site visits, valued at S\$200--400 opportunity cost (assuming S\$25--35/hr effective wage for a sole proprietor).
  \item \textbf{Effort reduced:} Eliminates need to cross-reference NEA tender PDFs, data.gov.sg licensing records, and MRT maps manually---three separate data sources consolidated into one score.
  \item \textbf{Risk avoided:} Over-bidding on NEA tender (lock-in at above-AMR rent for 3 years) or signing a coffeeshop lease at S\$5K--10K/mo in a low-footfall zone.
\end{itemize}

At 500 paying Starter subscribers, annual recurring revenue (ARR) = S\$174,000; at 2,000 subscribers, ARR = S\$696,000.

%==============================================================================
\section{Go-to-Market Difficulties}
\label{sec:gtm}
%==============================================================================

\noindent\textbf{Summary.} Building the pipeline is only half the battle. Promoting StallPulse to hawker entrepreneurs faces distinct commercial, trust, and operational obstacles. We analyze each honestly below.

\subsection{Trust and Adoption When Promoting the Product}

\textbf{Problem:} Hawker operators are skeptical of algorithmic scores from an unknown startup. They trust their own site visits and peer recommendations more than a dashboard.

\textbf{Impact on promotion:} High customer acquisition cost (CAC); long sales cycles; need for free trials or money-back guarantees before first payment.

\textbf{Mitigation:} Publish scoring methodology openly; link every score to underlying data.gov.sg records; partner with NEA CoC training providers to demo the tool during the mandatory business course; offer first report free.

\subsection{Customer Acquisition Channels and Cost}

\textbf{Problem:} Our target customers (sole proprietors) are not concentrated on LinkedIn or enterprise software marketplaces. They discover tools through word-of-mouth, CoC courses, and hawker association networks---channels that do not scale with typical B2B SaaS playbooks.

\textbf{Impact on promotion:} Cannot rely on Google Ads or content marketing alone; need ground-level partnerships (NEA, ITE CoC instructors, hawker associations) and referral incentives.

\textbf{Mitigation:} Embed StallPulse demo in CoC curriculum; sponsor hawker association newsletters; offer referral credit (one free month per referred operator).

\subsection{Data Acquisition Costs and Risks}

\begin{itemize}
  \item \textbf{NEA/SFA licensing data:} Free, open government data (Open Data Licence). Low acquisition cost.
  \item \textbf{AMR rent benchmarks:} Manually curated from NEA tender PDFs; not available via API. Requires periodic manual updates---a recurring labor cost that limits how fast we can expand coverage beyond 25 centres.
  \item \textbf{MRT proximity:} Free from LTA/data.gov.sg. GeoJSON download available.
  \item \textbf{Risk:} data.gov.sg rate limits (HTTP 429) during bulk ingestion; mitigated with backoff and batch scheduling.
\end{itemize}

\subsection{Legal, Privacy, and Platform Restrictions}

Licensed establishment data contains business names and addresses but not personal data of individuals. PDPA risk is low for B2B aggregated analytics. We do not scrape social media profiles or track individuals. data.gov.sg permits commercial use under the Singapore Open Data Licence. Reddit API blocked automated searches (HTTP 403) during our research script---a reminder that third-party platform ToS can block data collection channels.

\subsection{Cold-Start and Network Effects}

Scores improve with more granular competition data (cuisine type, operating hours). Initial MVP uses postal-prefix aggregation, which is coarse. \textbf{Chicken-and-egg:} operators want proven accuracy before paying; accuracy improves with more paying customers providing feedback on score quality. Promoting before we have user testimonials creates a credibility gap.

\subsection{Competition and Defensibility When Scaling Promotion}

\begin{itemize}
  \item \textbf{Incumbents:} Manual consultants (high touch, high price); NEA calculator (free, limited scope); Google Maps (reviews, no structured scoring).
  \item \textbf{Moat:} Proprietary scoring model tuned on Singapore hawker economics; curated AMR dataset; integration with NEA tender calendar (future feature).
  \item \textbf{Threat:} Google or Grab could add location scores; a well-funded competitor could replicate our pipeline from the same public data. Differentiation must come from hawker-specific features, local rent data curation, and distribution partnerships---not data exclusivity.
\end{itemize}

\subsection{Unit Economics of Promotion at Scale}

\begin{table}[H]
\centering
\caption{Unit economics sketch (monthly, at steady state)}
\label{tab:unit}
\begin{tabular}{@{}lrrr@{}}
\toprule
\textbf{Scale} & \textbf{Subscribers} & \textbf{Revenue} & \textbf{Infra Cost} \\
\midrule
Initial & 50 & S\$1,450 & S\$50 (Vercel + Neon) \\
10$\times$ & 500 & S\$14,500 & S\$200 \\
100$\times$ & 5,000 & S\$145,000 & S\$1,500 \\
\bottomrule
\end{tabular}
\end{table}

Gross margin exceeds 85\% at scale, but \textbf{customer acquisition}---not compute---is the binding cost. If CAC exceeds S\$100 per Starter subscriber (typical for partnership-driven B2B SME sales), payback period is $\sim$3--4 months at S\$29/mo, which is acceptable but requires disciplined channel selection.

%==============================================================================
\section{System Design}
%==============================================================================

\subsection{Overview}

StallPulse implements a classic \textbf{batch analytics pipeline} with a \textbf{web delivery layer}:

\begin{enumerate}
  \item \textbf{Ingestion} --- Python scripts fetch data from data.gov.sg REST APIs.
  \item \textbf{Storage} --- Raw CSV/JSON in local/cloud object storage; processed Parquet for analytics.
  \item \textbf{Processing} --- Pandas batch job computes viability scores (Spark-compatible design for scale).
  \item \textbf{Delivery} --- Next.js app on Vercel serves dashboard and REST API.
\end{enumerate}

\subsection{Data Sources}

\begin{table}[H]
\centering
\caption{Data sources and ingestion method}
\begin{tabular}{@{}lllr@{}}
\toprule
\textbf{Dataset} & \textbf{Source} & \textbf{Method} & \textbf{Rows} \\
\midrule
Licensed eating establishments & data.gov.sg / NEA & REST API (paginated) & 36,687 \\
MRT station names & data.gov.sg / LTA & REST API & 184 \\
Hawker centre AMR rents & NEA tender notices & Curated CSV & 25 \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Storage and Processing}

\begin{itemize}
  \item \textbf{Raw layer:} CSV and JSON files (\texttt{data/raw/}) --- analogous to a distributed file system (HDFS/S3) for immutable raw dumps.
  \item \textbf{Processed layer:} Apache Parquet (\texttt{data/processed/}) --- columnar format for efficient analytics queries; production would use PostgreSQL (Neon) or BigQuery.
  \item \textbf{Processing:} Python/Pandas batch job (\texttt{scripts/process/score\_locations.py}). At 100$\times$ scale, migrate to Apache Spark on Dataproc or EMR for parallel postal-prefix aggregation across 36K+ records.
  \item \textbf{Message queue (future):} Apache Kafka would trigger re-scoring when data.gov.sg publishes monthly NEA updates, decoupling ingestion from processing.
\end{itemize}

\subsection{Scoring Model}

Viability score (0--100) is a weighted composite:
\begin{align*}
  S = 0.35 &\cdot f_{\text{footfall}} + 0.25 \cdot f_{\text{competition}} + 0.20 \cdot f_{\text{rent}} \\
           &+ 0.10 \cdot f_{\text{hygiene}} + 0.10 \cdot f_{\text{density}}
\end{align*}

where $f_{\text{footfall}}$ is derived from MRT distance, $f_{\text{competition}}$ from licensed establishment density by postal prefix, $f_{\text{rent}}$ from AMR relative to market median, $f_{\text{hygiene}}$ from average NEA grade in the area, and $f_{\text{density}}$ from estimated stall capacity.

\subsection{Delivery}

\begin{itemize}
  \item \textbf{Web dashboard:} Next.js 16 + React + Tailwind CSS --- interactive ranked list with score breakdown.
  \item \textbf{REST API:} \texttt{GET /api/locations?area=\&min\_score=\&q=} --- JSON feed for Pro subscribers.
  \item \textbf{Future:} PDF location reports, NEA tender alert emails, embedded widget for CoC course portals.
\end{itemize}

\subsection{Architecture Diagram}

\begin{figure}[H]
\centering
\begin{tikzpicture}[
  node distance=1.2cm and 1.8cm,
  box/.style={draw, rounded corners, minimum width=2.8cm, minimum height=0.9cm, align=center, font=\small},
  store/.style={box, fill=blue!10},
  proc/.style={box, fill=orange!15},
  deliver/.style={box, fill=green!12},
  arrow/.style={-{Stealth[length=2mm]}, thick}
]
  \node[box, fill=gray!15] (dg) {data.gov.sg\\NEA + LTA APIs};
  \node[store, right=of dg] (raw) {Raw Storage\\CSV / JSON};
  \node[proc, right=of raw] (batch) {Batch Processor\\Pandas / Spark};
  \node[store, right=of batch] (parq) {Processed\\Parquet + JSON};
  \node[deliver, below=1.5cm of parq] (vercel) {Next.js on Vercel\\Dashboard + API};
  \node[box, fill=gray!15, left=of vercel] (user) {Customer\\Hawker / F\&B Op};

  \draw[arrow] (dg) -- (raw) node[midway, above, font=\tiny] {ingest};
  \draw[arrow] (raw) -- (batch) node[midway, above, font=\tiny] {batch job};
  \draw[arrow] (batch) -- (parq);
  \draw[arrow] (parq) -- (vercel) node[midway, right, font=\tiny] {deploy};
  \draw[arrow] (vercel) -- (user) node[midway, below, font=\tiny] {HTTPS};
\end{tikzpicture}
\caption{StallPulse end-to-end architecture}
\label{fig:arch}
\end{figure}

\subsection{Scalability and Cost at 10$\times$ and 100$\times$}

\textbf{10$\times$ (500 subscribers, 250 centres):}
\begin{itemize}
  \item Migrate batch processing to Apache Spark (local $\rightarrow$ 4-node cluster).
  \item Store processed data in PostgreSQL (Neon serverless) instead of static JSON.
  \item Add Redis cache for API hot queries.
  \item Estimated infra: S\$200/month.
\end{itemize}

\textbf{100$\times$ (5,000 subscribers, 1,000+ centres):}
\begin{itemize}
  \item Stream NEA updates via Kafka; incremental scoring with Spark Structured Streaming.
  \item Data lake on S3/GCS with Parquet partitioning by planning area.
  \item CDN for static reports; API rate limiting via API gateway.
  \item Estimated infra: S\$1,500/month vs.\ S\$145,000 MRR (99\% gross margin).
\end{itemize}

%==============================================================================
\section{Repository and Deployment}
%==============================================================================

The project repository contains:
\begin{itemize}
  \item \texttt{scripts/ingest/} --- data.gov.sg ingestion scripts
  \item \texttt{scripts/process/} --- batch scoring pipeline
  \item \texttt{scripts/demand-research/} --- demand evidence collection
  \item \texttt{web/} --- Next.js delivery application
  \item \texttt{data/} --- raw and processed sample data
  \item \texttt{report/report.tex} --- this document
\end{itemize}

Deploy the web app to Vercel by pointing the project root to \texttt{web/}. See \texttt{VERCEL.md} for step-by-step instructions.

%==============================================================================
\section{Conclusion}
%==============================================================================

StallPulse demonstrates that public government data, when refined through a batch analytics pipeline and delivered via a focused SaaS product, can address a real and monetizable need. Section~\ref{sec:customer} identifies hawker stall entrepreneurs as the target wedge. Section~\ref{sec:demand} documents a six-step data-acquisition process from hypothesis to WTP estimate. Section~\ref{sec:wtp} quantifies monetary (S\$29--99/mo), time (8--12 hrs/mo saved), and effort (manual cross-referencing eliminated) investment. Section~\ref{sec:gtm} analyzes promotion difficulties including trust, channel access, cold-start, and customer acquisition cost. Technical risks (rate limits, coarse geocoding) are manageable with transparent sourcing and iterative model improvement.

\end{document}
